IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-07-08 paper/real.tex
nits

While the described system implements |specLangJS seqf|, server-side
applications may require access to the file system, HTTP server, HTTP
client, etc.
%
Unfortunately, our formalism does not capture such external effects
and exposing the Node.js libraries directly to sandboxed tasks is unsafe.
%
We, instead, implement libraries such as a labeled file system as
message exchanges between the sandboxed tasks (e.g., \textsf{task-1}
in Figure~\ref{fig:node}) and the main Node.js task that implements
our IFC monitor.\footnote{
  Importantly, our libraries provide mostly-identical interfaces to
  the standard Node.js libraries, hiding the underlying
  message-passing implementations.
}
%
(This is safer than the approach of simply wrapping objects, which can
potentially allow for accessing objects outside the context.)
%
This task is trusted to ensures that, for instance, labels are
propagated to files and the labels of the task performing the
operations and the file in question are inspected appropriately, as to
preserve non-interference.
%
Unfortunately, while imposing such a proof burden on the
framework developer is undesirable, this is also somewhat expected:
different language environments expose different libraries for
handling external I/O.
%
For instance, in the case of Node.js, how labels interact with the
file system may even vary according to the application (e.g.,
different from our implementation, Hails~\cite{hails} does not persist
labels).
%
While we can extend our formalism to model a particular interface to
the file system, HTTP client, etc. the applicability of this are
unclear and left to future work.
%

@@

Most notably, tasks in COWL usually correspond to browsing contexts,
such as iframes.
%
Hence, the global object |tS0| also contains the DOM, the
\verb|XMLHttpRequest| (XHR) object, etc.
%
To ensure that JavaScript code cannot communicate using these objects
(e.g., to the network with XHR or persistent storage using the DOM),
COWL additionally uses content security policy (CSP)~\cite{csp1.1}.\footnote{
  Since CSP does not yet address message passing or navigation, this
  was addressed explicitly.
}
%
Note, that this does not prevent tasks from manipulating the DOM
(e.g., to render information).
%
Rather, to enforce task-isolation, external effects due to DOM access
are suppressed.

>>>>

While the described system implements |specLangJS seqf|, server-side
applications may require access to the file system, HTTP server, HTTP
client, etc.
%
Unfortunately, our formalism does not capture such external effects
and exposing the Node.js libraries directly to sandboxed tasks is unsafe.
%
We, instead, implement libraries such as a labeled file system as
message exchanges between the sandboxed tasks (e.g., \textsf{task-1}
in Figure~\ref{fig:node}) and the main Node.js task that implements
our IFC monitor.\footnote{
  Importantly, we provide mostly-identical interfaces to
  the standard Node.js libraries, hiding the underlying
  message-passing implementations.
}
%
(This is safer than the approach of simply wrapping objects, which can
potentially allow for accessing objects outside the context.)
%
This task is trusted to ensures that, for instance, labels are
propagated to files and the labels of the task performing the
operations and the file in question are inspected appropriately, as to
preserve non-interference.
%
Unfortunately, while imposing such a proof burden on the
framework developer is undesirable, this is also somewhat expected:
different language environments expose different libraries for
handling external I/O.
%
For instance, in the case of Node.js, how labels interact with the
file system may even vary according to the application (e.g.,
different from our implementation, Hails~\cite{hails} does not persist
labels).
%
While we can extend our formalism to model a particular interface to
the file system, HTTP client, etc. the applicability of this are
unclear and left to future work.
%

@@

Most notably, tasks in COWL usually correspond to browsing contexts,
such as iframes.
%
Hence, the global object |tS0| also contains the DOM, the
\verb|XMLHttpRequest| (XHR) object, etc.
%
To ensure that JavaScript code cannot communicate using these objects
(e.g., to the network with XHR or persistent storage using the DOM),
COWL additionally uses content security policy (CSP)~\cite{csp1.1}.\footnote{
  Since CSP does not yet restrict message-passing or navigation, this
  was addressed explicitly.
}
%
Note, that this does not prevent tasks from manipulating the DOM
(e.g., to render information).
%
Rather, to enforce task-isolation, external effects due to DOM access
are suppressed.
